%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Vitor Pereira Bezzan} \\[7.5pt]
\href{https://github.com/vitorbezzan}{\raisebox{-0.05\height}\faGithub\ vitorbezzan} \ $|$ \
\href{https://www.linkedin.com/in/vbezzan}{\raisebox{-0.05\height}\faLinkedin\ vbezzan} \ $|$ \
\href{https://bezzan.com}{\raisebox{-0.05\height}\faGlobe \ bezzan.com} \ $|$ \
\href{mailto:vitor@bezzan.com}{\raisebox{-0.05\height}\faEnvelope \ vitor@bezzan.com} \ $|$ \
\href{tel:+5511943044111}{\raisebox{-0.05\height}\faMobile \ +55 11 94304-4111} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Strong background in heavy industries, including oil and gas, mining, agriculture, chemicals and energy.

I am skilled in leveraging cutting-edge technologies and advanced data analysis techniques to drive actionable insights and deliver impactful solutions. Specialized in machine learning, time series analysis, high-performance computing, and software development.

Throughout my career, I have successfully led and executed numerous data-driven projects, enabling organizations to optimize operations, enhance efficiency, and make informed business decisions. By applying my expertise in machine learning algorithms and statistical modeling, I have developed predictive models that have significantly improved production forecasting, asset management, and supply chain optimization.

I possess strong software development skills, enabling me to create custom tools and solutions that integrate seamlessly into existing infrastructure. By collaborating closely with cross-functional teams, I have successfully translated business requirements into practical solutions, leading to millions of dollars in sustainable business impact.

%Experience
\section{Work Experience}

\begin{jobshort}{Principal DS II at \textit{McKinsey and Company}}{Nov 2017 - current}
Through my expertise in predictive maintenance, plant process set-point optimization, and MLOps at scale,
I have successfully implemented cutting-edge solutions that have generated millions of dollars in value.
By leveraging advanced analytics techniques, I have enabled organizations to optimize maintenance schedules, reduce
downtime, and enhance operational efficiency.

Working hand-in-hand with teams, I drive the deployment of data-driven insights to revolutionize processes within the
sector. By understanding the unique challenges faced by companies in these domains, I develop tailored solutions that
deliver tangible business outcomes.
\end{jobshort}

\begin{jobshort}{Principal DS I at \textit{McKinsey and Company}}{Aug 2021 - Aug 2024}
Developed my career through mobility and had the opportunity to live and work in London for 3 years.
Also did projects in Switzerland, Australia and Canada during this time.
\end{jobshort}

\begin{jobshort}{IB Senior Analyst, DS at \textit{Banco Safra S/A}}{Nov 2014 - Nov 2017}
Developed a myriad of different models and solutions to enable several different areas of the
IB business. Worked closely with CRM, modelling, credit/market risk and asset management teams.
\end{jobshort}

\begin{jobshort}{Business Analyst at \textit{Deloitte LLP}}{Sep 2011 - Jan 2013}
Started my career as a BA for Deloitte. Also had an opportunity to work and live in Chicago to
develop and refine technology solutions using analytics for healthcare and finance.
\end{jobshort}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2030 - present & PhD (Subject) at \textbf{University} \hfill \normalsize (GPA: 4.0/4.0) \\

2023 - 2027 & Bachelor's Degree at \textbf{College} \hfill (GPA: 4.0/4.0) \\ 

2022 & Class 12th Some Board \hfill  (Grades) \\

2021 & Class 10th Some Board \hfill  (Grades) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Some Skills &  \normalsize{This, That, Some of this and that etc.}\\
Some More Skills  &  \normalsize{Also some more of this, Some more that, And some of this and that etc.}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
